---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# congressapi

<!-- badges: start -->
[![R-CMD-check](https://github.com/miriamasagold/congressapi/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/miriamasagold/congressapi/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/miriamasagold/congressapi/branch/main/graph/badge.svg)](https://app.codecov.io/gh/miriamasagold/congressapi?branch=main)
<!-- badges: end -->
<img src='man/figures/logo.svg' align="right" height="138.5" />

**congressapi** provides an extremely lightweight wrapper, facilitating seamless data retrieval from the [official Congress API](https://api.congress.gov/) via a single function, `get_congress()`.

## Installation

You can install the development version of **congressapi** from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("miriamasagold/congressapi")
```

## Retrieving data

Data may be retrieved from one of eleven base endpoints:

* bill
* amendment
* summaries
* congress
* member
* committee
* committee-report
* congressional-record
* house-communication
* nomination
* treaty

All the user needs to do is specify the endpoint, along with any additional specifications desired:

```{r congressGet}
library(congressapi)
# Retrieves all house bills from the 117th Congress
bill <- 
    dplyr::tibble(
      congressapi::get_congress("bill/117/hr")
      )

head(bill)

```

Visit https://miriamasagold.github.io/congressapi/ to read full package documentation. If you find a bug or would like to see a new functionality, please submit an [issue](https://github.com/miriamasagold/congressapi/issues).

# Note

This project is neither endorsed nor sponsored by the United States Congress.
