---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# congressapi

<!-- badges: start -->
<!-- badges: end -->

The goal of congressapi is to facilitate seamless data retrieval from the [official Congress API](https://api.congress.gov/) by providing a single wrapper function, `congressGet()`.

## Installation

You can install the development version of **congressapi** from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AMGold99/congressapi")
```

## Retrieving data

Data may be retrieved from one of eleven base endpoints:

* bill
* amendment
* summaries
* congress
* member
* committee
* committeeReport
* congressional-record
* house-communication
* nomination
* treaty

All the user needs to do is specify the endpoint, along with any additional specifications desired:

```{r congressGet}
library(congressapi)

# congress_set_key()

# Retrieves all house bills from the 117th Congress
bill <- congressGet("bill/117/hr")

head(bill)

```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
