---
title: "congressapi"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{congressapi}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

```

# Set Up

The package **congressapi** allows you to retrieve data from eleven different [Congress API](https://api.congress.gov/) endpoints, returning (most) as data frames by default.

To set up your session, request an API key [here](https://api.congress.gov/sign-up/). Then use `congress_set_key()` to save that key to your R session.

```{r setup-key}
library(congressapi)

api_key <- "YOUR_API_KEY_HERE"

congress_set_key(api_key)

```

```{r secret-set-up, include = FALSE}
library(dplyr)
library(utils)
library(purrr)
congress_set_key("Q4sx4JhmbiXxePlys49UyztTbiUDkaRkERT3sPKW")
```

# Retrieving Data

You may request data from eleven unique endpoints:

* bill
* amendment
* summaries
* congress
* member
* committee
* committeeReport
* congressional-record
* house-communication
* nomination
* treaty

Here is a basic call to `congressGet()`.

```{r}
member <- congressGet("member")
member_tbl <- dplyr::tibble(member)

head(member_tbl)
```

## Limits and Pagination

By default, the API returns 20 observations per request. To adjust the amount of data returned, you may pass the `limit` argument to `congressGet()`:

```{r}
rows <- 50

bill <- congressGet("bill", limit = rows)

nrow(bill) == rows
```
To paginate results, use `offset`. Because each page returns 20 observations, an offset of 20 will return the second page, 40 will return the third, and so on. Combining this feature with a functional paradigm provides a pleasant method of collating multiple pages into a single data frame.

```{r}
# Should return 60-row data frame
offsets <- c(20, 40, 60)

three_pages <-
  purrr::map_dfr(
    .x = offsets,
    .f = ~ congressGet("bill",
                       offset = .x)
  )

nrow(three_pages)

```
Note that, because additional arguments like offset and limit are passed via dots, they must be named for the server to understand what their values refer to.

## Additional Parameters

In addition to offset and limit, several additional parameters may be passed to the GET request via `congressGet()`. These include `sort` (either `"asc"` or `"desc"`), `fromDateTime`, and `toDateTime` (full timestamps required). 

Note that many endpoints, like bill, allow you to explicitly specify a congressional session in the main endpoint path (e.g., `"bill/117"`). In some cases, this may be preferable to timestamp customization.

## Endpoint Paths

Within each endpoint, a variety of more specialized paths may be specified. For instance, to retrieve detailed information on a specific member, you can add a [BioGuide ID](https://www.congress.gov/help/field-values/member-bioguide-ids). Below, note the warning message. Some endpoints cannot be coerced into dataframes and will instead return the content of the API request.

```{r}
single_member <- congressGet("member/S000033")

utils::str(single_member)
```

To find a complete reference of all valid endpoint paths, visit the [Congress API webpage](https://api.congress.gov/)



